\documentclass[9pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.92]{geometry}

\firstname{Carlos Guillermo}
\familyname{Ledezma Rondon}
\mobile{+61 424338978}
\email{cgledezma1101@gmail.com}

\begin{document}
\makecvtitle{}

I am a software developer that's passionate about code quality, and solving
problems at large scale. When looking for a role, I want a place where I get to
tackle complex challenges. I love working alongside teammates that help me see
all the aspects of a solution that I had not considered, and with whom I can
delight my customers even more than what could've been done individually.

\section{Work experience}

\cventry{2021 --}{Senior software development engineer}{Amazon Web Services}{Sydney, Australia}{}{}
\cventry{2018 -- 2021}{Software development engineer}{Amazon Web Services}{Sydney, Australia}{}{}
\cvitem{Technologies}{AWS, CloudFormation/CDK, Kotlin, Gradle, TestNG, NodeJS,
    ReactJS, Typescript, Jest, Git.}

Key achievements:

\cvlistitem{Worked with a team of around 20 engineers to build
    \href{https://aws.amazon.com/about-aws/whats-new/2021/05/introducing-incident-manager-aws-systems-manager/}{AWS
        Systems Manager Incident Manager} from scratch.}
\cvlistitem{Designed, planned, and led the development of the data storage abstraction that
    supports the multi-region replication at the heart of Incident Manager.}
\cvlistitem{Designed and led the development of the integration between Incident Manager
    and PagerDuty.}
\cvlistitem{Led the development of a user interface that internal teams could leverage to
    track impact of events on internal services. This tool leveraged APIs that were
    built by my same team.}
\cvlistitem{All throughout my experience I've developed a wide toolset of operational
    practices that allow me to design and build services that can perform at
    a large scale, without sacrificing quality.}
\cvlistitem{Helped engineers grow in their roles to achieve successful promotions.}

\cventry{2014 -- 2018}{Full-stack engineer}{WiseTech Global}{Sydney, Australia}{}{}
\cvitem{Technologies}{C\#, Javascript, NUnit, Jasmine, HTML, CSS, WPF, TFS.}

Key achievements:

\cvlistitem{Led the modernization of one of the company's core internal components. This involved a full rewrite of the
    tool's interface from Windows Forms to HTML, CSS, and JS, as well as rewriting some of the core backend components
    to make them more compartmentalized and reusable}
\cvlistitem{Successfully implemented a company-wide library that allows developers to
    localize strings. This included validations that made sure no new non-localized
    strings were introduced in the code.}
\cvlistitem{Implemented a library that allowed the company's main product, CargoWise One,
    to automatically scale its interface to screens of different resolutions.}

\cventry{2013 -- 2014}{Full-stack engineer}{Akdemia}{Caracas, Venezuela}{}{}
\cvitem{Technologies}{Ruby, Ruby on Rails, Javascript, HTML, CSS, Git.}

Key achievements:

\cvlistitem{Mapped out full database structure from Ruby on Rails models in order to understand points of improvement.}
\cvlistitem{Led customer meetings where I helped determine the path forward for the product.}

\section{Education}
\cventry{2008 -- 2014}{Bachelor's of science in software engineering}{Universidad Simón Bolívar}{Caracas, Venezuela}{}{}
\cventry{2012 -- 2013}{Exchange studies in software engineering}{Royal Institute of Technology}{Stockholm, Sweden}{}{}
\cventry{1997 -- 2008}{High school diploma}{U.E. Colegio Claret}{Caracas, Venezuela}{}{}

\section{Additional information}
\cvitem{Languages}{English (fluent), Spanish (fluent), French (basic).}
\cvitem{GitHub}{https://github.com/cgledezma1101}
\cvitem{LinkedIn}{https://au.linkedin.com/in/cgledezma}
\cvitem{Hobbies}{Certified PADI rescue diver, current coach of UNSW's underwater rugby team, amateur photographer.}

\end{document}